Concurrent Priority Queues

### 2014-03-29 presentation/presentation.Rnw
Linden slides

\begin{frame}{\nameref{sec:lockfree}}
\framesubtitle{\citeauthor{linden2013skiplist}}
% TODO: Short summary only?
\begin{itemize}
\item
\end{itemize}
\end{frame}

@@

>>>>

@@

\begin{itemize}
\item Most efficient strict \ac{PQ}, \ac{SL}-based \& linearizable
\item Concurrent strict \ac{PQ} performance limited by contention and \ac{CAS} failures in
      \lstinline|DeleteMin| \textrightarrow ~ Minimize \ac{CAS} calls
\item Deleted nodes form prefix of \ac{SL}, deletion flag packed into \lstinline|next| pointer of
      \emph{previous} node prevents insertion \emph{before} deleted node
\item Most \lstinline|DeleteMin| perform logical deletion (1 \ac{CAS}) only, physical deletion
      only once a bound is reached
\item Improves upon best previous \acp{PQ} by up to factor 2
\item \fullcite{linden2013skiplist}
\end{itemize}
\end{frame}

\begin{figure}
\includegraphics[width=\textwidth]{linden}
\caption{The \citeauthor{linden2013skiplist} \ac{PQ}. Concurrent \lstinline|Insert(3)| and
\lstinline|DeleteMin| operations. Top right: \lstinline|DeleteMin| succeeds first,
\lstinline|Insert(3)| \ac{CAS} fails. Bottom right: \lstinline|Insert(3)| succeeds first,
\lstinline|DeleteMin| returns 3. (Image source: \cite{linden2013skiplist})}
\end{figure}
\end{frame}
